\TheTitle

### 2017-07-14 paper/study.tex
editing: study procedure

The study begins with a short introduction to the \mt model, followed by
an introduction to Gitk and \tool. We provided two examples of
converting the DAG to the \mt. The first DAG was a flat merge, so the
corresponding merge tree did not have any internal nodes. The second was
not a flat merge, so the corresponding merge tree contained a single
internal node. Any questions about the model were answered at this time.
Following the introduction to the \mt model, we introduce Gitk and
\tool, providing information about what each pane shows in Gitk, and
what each tab does in \tool.

The conceptual tasks follow the introduction, followed by the
summarization, which are then followed by the user opinion. The study is
completed with three questions to enable us to know more about the
participants;

@@

To mitigate the order bias cased by using one tool before the other or
one commit before the other, we randomize both the tool and commit
between participants. The conceptual tasks are run twice, once with
\comA and once with \comB, in the same order for all participants using
the git tools.

\evan{This paragraph is kind of tricky to explain well. See if you can
  understand what I'm trying to say} The summarization tasks are run
four times, once with \comA and \tool, \comB and \tool, \comA and git
tools, and \comB and git tools. The participant will start with one
tool, and complete the tasks for both commits in that tool. The order of
the commits is the same as in the conceptual tasks. Once they complete
the summarization tasks for both \comA and \comB, they will switch to
the other tool and complete the tasks again on the commits in the same
order. The order of the tasks is consistent for all four runs.

The user opinions do not directly involve working with the tools or the
commits, so the ordering of the tools

% To mitigate the order bias caused by using one tool before the other,
% one commit before the other, and the various tasks, we randomize...

We use a script written in python 3.6.1 in order to assure that we do no
bias the randomization, and ensure that correct ordering is maintained
between tools, tasks, and commits. The script produces the entire script
for the study, so we only need to read it to correctly conduct the
study. Re-running the script generates the study for the next
participant. We use screen capture to record the audio and video. From
the screen capture, we measure the time, as well as recording the
responses in the study.

\evan{Should I include the python script? It would make explaining how
  the test was conducted 100\% clear.}

% TODO: maybe move the time measuring procedure from summ. to here

>>>>

The study begins with a short introduction to the \mt model, followed by
an introduction to Gitk and \tool. We provided two examples of
converting the DAG to the \mt. The first example DAG was a flat merge,
so the corresponding \mt did not have any internal nodes. The
second was not a flat merge, so the corresponding \mt contained a
single internal node. Any questions about the model were answered at
this time. Following the introduction to the \mt model, we introduce
Gitk and \tool, providing information about what each pane shows in
Gitk, and what each tab does in \tool.

The conceptual tasks follow the introduction, followed by the
summarization, which are then followed by the user opinion. The study is
concluded with three questions to enable us to learn more about the
participants;

@@

To mitigate the order bias cased by using one tool before the other or
one commit before the other, we randomize both the order that the tools
are used, and the order that the commits are used, between participants.
The conceptual tasks are run twice, once with \comA and once with \comB,
in the same order for all participants using the git tools.

\evan{This paragraph is kind of tricky to explain well. See if you can
  understand what I'm trying to say} The summarization tasks are run
four times, once with \comA and \tool, \comB and \tool, \comA and git
tools, and \comB and git tools. The participant will start with one
tool, and complete the tasks for both commits in that tool. The order of
the commits is the same as in the conceptual tasks. Once they complete
the summarization tasks for both \comA and \comB, they will switch to
the other tool and complete the tasks again on the commits in the same
order. The order of the tasks is consistent over all four runs. The
questions in the user opinions section do not directly involve the tools
or commits.

We use a script written in python 3.6.1 in order to assure that we do
not bias the randomization, and ensure that correct ordering is
maintained between tools, tasks, and commits. The script produces the
entire script for the study, so we only need to read it to correctly
conduct the study. Re-running the script generates the study for the
next participant. We use screen capture to record the audio and video.
From the screen capture, we measure the time, as well as recording the
responses in the study.

\evan{Should I include the python script? It would make explaining how
  the test was conducted 100\% clear.}
\evan{I think it would be far too long then.}
